Results_setup

### 2020-06-04 src/Result_Setup.Rmd
updates from final v2 files

glm.female.strain.subsp <- glm(mean_co ~ subsp * strain, data= female_mouse.avs_for.analysis)

@@

MLH1.female.spc.glm.M2 <- glm(mean_co ~ strain, data= female_mouse.avs_for.analysis)
sum_MLH1.female.spc.glm.M2 <- summary(MLH1.female.spc.glm.M2)

@@

```{r Male.specific.glm, echo=FALSE, eval=TRUE}

#these are M4
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data= male_mouse.avs_for.analysis)
sum_MLH1.male.glm.M4 <- summary(MLH1.male.glm.M4)
#round(summry.male.strain.effects$coefficients[,c(1,4)], 5)

#sum_MLH1.male.specific.glm.M2$coefficients[5,][4]

#PWD, SKIVE, MSM
#8,9,10

@@

#M4.2
MLH1.male.glm.M4.2 <- glm(mean_co ~ strain, data= male_mouse.avs_for.analysis)
sum_MLH1.male.glm.M4.2 <- summary(MLH1.male.glm.M4.2)

@@

@@

t.test_mouse.av.IFD_PER_MOL <- t.test(  (mouse.level.BivData_table %>% filter(Rec.group == "1") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$mean_IFD.2CO_PER,
   (mouse.level.BivData_table %>% filter(Rec.group == "0") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$mean_IFD.2CO_PER   )

@@

t.test_mouse.av.IFD_ABS_MOL <- t.test(  (mouse.level.BivData_table %>% filter(Rec.group == "1") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus"))$mean_IFD.2CO_ABS,
   (mouse.level.BivData_table %>% filter(Rec.group == "0") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$mean_IFD.2CO_ABS  )
```

>>>>

glm.female.strain.subsp <- glm(mean_co ~ subsp * strain, data= (female_mouse.avs_for.analysis %>% filter(subsp != "Cast") ) )

@@

MLH1.female.spc.glm.M2 <- glm(mean_co ~ strain, data= (female_mouse.avs_for.analysis %>% filter(subsp != "Cast") ) )
sum_MLH1.female.spc.glm.M2 <- summary(MLH1.female.spc.glm.M2)

@@

```{r Male.specific.glm, echo=FALSE, eval=TRUE}
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data=(male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") )   )

sum_MLH1.male.glm.M4 <- summary(MLH1.male.glm.M4)
#PWD, SKIVE, MSM
#8,9,10

@@

#M4.2
MLH1.male.glm.M4.2 <- glm(mean_co ~ strain, data= (male_mouse.avs_for.analysis  %>% filter(subsp != "Cast") ))
sum_MLH1.male.glm.M4.2 <- summary(MLH1.male.glm.M4.2)

@@

```{r Q2.IFD.setup, echo=FALSE}

#identify and remove mice with 1 bivalent observation (MSM:  1feb18_MSM_m1)
#some cells just have 1 cell, but the MSM_m is the only with just 1 bivlent

@@

@@

#niether PER or ABS is sig, 1 mouse, #1feb18_MSM_m1 has only 1 observation

t.test_mouse.av.IFD_PER_MOL <- t.test(  (mouse.level.BivData_table %>% filter(Rec.group == "1") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(mouse != "1feb18_MSM_m1")   )$mean_IFD.2CO_PER,
   (mouse.level.BivData_table %>% filter(Rec.group == "0") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$mean_IFD.2CO_PER   )

t.test_mouse.av.IFD_ABS_MOL <- t.test(  (mouse.level.BivData_table %>% filter(Rec.group == "1") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(mouse != "1feb18_MSM_m1") )$mean_IFD.2CO_ABS,
   (mouse.level.BivData_table %>% filter(Rec.group == "0") %>% filter(sex == "male") %>% filter(subsp == "Mol") )$mean_IFD.2CO_ABS  )

```{r Q2.show.IFD.Mol, echo=FALSE}

#mouse.level.BivData_table
#cleanCurated_BivData

#molossinus does not show

Musc.IFD.Biv <- ggplot(data = (cleanCurated_BivData %>% filter(subsp == "Musc") %>% filter(sex == "male") %>% filter(hand.foci.count == 2)  ), aes(x = strain, y = IFD1_PER) ) + geom_jitter()

Mol.IFD <- ggplot(data = (cleanCurated_BivData %>% filter(subsp == "Mol") %>% filter(sex == "male") %>% filter(hand.foci.count == 2)  ), aes(x = strain, y = IFD1_PER) ) + geom_jitter() +facet_wrap(~mouse)

t.test_biv.av.IFD_PER_MOL <- t.test(  (cleanCurated_BivData %>% filter(Rec.group == "1") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$IFD1_PER,
   (cleanCurated_BivData %>% filter(Rec.group == "0") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$IFD1_PER   )
#p value for the bivalent level IFD1 norm positions are significant

#mouse level
t.test_mouse.av.IFD_PER_MOL <- t.test(  (mouse.level.BivData_table %>% filter(Rec.group == "1") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$mean_IFD.2CO_PER,
   (mouse.level.BivData_table %>% filter(Rec.group == "0") %>% filter(sex == "male") %>% filter(subsp == "Mol") %>% filter(species == "M.musculus") )$mean_IFD.2CO_PER   )

#1feb18_MSM_m1

Mol.mus.IFD <- ggplot(data = (mouse.level.BivData_table %>% filter(subsp == "Mol") %>% filter(sex == "male")   ), aes(x = strain, y = mean_IFD_PER, color = mouse) ) + geom_jitter()
#there is mouse MSM with v low, 1feb18_MSM_m1 -- it only has 1 measure
